### 2020-03-01 defesa/tex/chapter/introducao.tex
wip

In \citeonline{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximal Covering Location Problem} was introduced. Unlike its predecessor, this version of the problem was not defined on graphs. Instead, on PMCLP the demand set and the facilities are located in $\R^2$ and a facility's coverage area is determined by a distance function. 
Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP and then utilize any of the previous developed exact methods to obtain a solution for PMCLP. This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, such that the optimal solution could be found. From the CLS, a network was built on which MCLP could be applied. Generating the CLS specifically for the case of Euclidean distance will be described here on \autoref{chapter:pmclp}.

@@

Two versions of PMCLP are studied in this work, both of them related to ellipses. The first one was introduced in \citeonline{canbolat} and will be referred to here as \sigla{PMCE}{Planar Maximal Covering by Ellipses}. This version does not allow the ellipses to rotate, so basically it only differs from its disks counterpart in the shape of the facility's coverage area. The second version was introduced in \citeonline{andreta} and will be referred to here as \sigla{PMCER}{Planar Maximal Covering by Ellipses with Rotation}. This version of the problem had no restriction on the rotation of ellipses--note that this is a slightly bigger modification of PMCLP compared to the first one, as not only the location for the facilities must be determined, but also their angle of rotation.
The main motivation to study these two versions of PMCLP is that cellphone towers can have elliptically shaped coverage area, therefore, to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by their signal, an elliptical PMCLP is better-suited \cite{canbolat}.

Only two articles have been found published in the literature that study this problem. In \citeonline{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem. For some instances, the method took too long and did not find an optimal solution. For this reason, a heuristic method was developed using a technique called Simulated Annealing. Solutions for the instances that timed-out with the first method were then obtained. The problem was further explored in \citeonline{andreta} which proposed a deterministic method that showed better performance obtaining optimal solutions for the instances, which the first method could not. Also, in \citeonline{andreta}, the version of the problem where the ellipses could be freely rotated was introduced and an exact method, which could not find optimal solutions for large instances; and a heuristic method were proposed for it. Despite the similarities, none of the works cited above base their development on the maximum covering by disks algorithms found in the literature.

The main results of this work are found in \autoref{chapter:ellipses_n} where a new algorithm for the version of the elliptical PMCLP where the ellipses can be freely rotated is developed. The proposed algorithm has a runtime complexity of $\bigO(n^{3m})$ and one of its most important steps is finding every solution of a not-previously-known problem. In \autoref{chapter:e3p}, this problem is introduced and an algorithm for it is presented. The rest of the work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied and a $\bigO(n^{2m})$ algorithm is proposed; in \autoref{chapter:ellipses}, the maximum covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents a conclusion as well as what is left as future work. Also, \autoref{chapter:ellipses_intersection} determines with detail the intersection of two ellipses, which is used in the algorithm developed in \autoref{chapter:ellipses}.

>>>>

In \citeonline{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximal Covering Location Problem} was introduced. Unlike its predecessor, this version of the problem was not defined on graphs. Instead, on PMCLP, the demand set and the facilities are located in $\R^2$, and a facility's coverage area is determined by a distance function.
Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP and then utilize any of the previous developed exact methods to obtain a solution for PMCLP. This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, such that the optimal solution could be found. From the CLS, a network was built on which MCLP could be applied. Generating the CLS specifically for the case of Euclidean distance will be described here on \autoref{chapter:pmclp}.

@@

We study two versions of PMCLP with elliptical coverage facilities in this work. For both of them, each ellipse is defined to have a fixed shape and an undefined location, which is part of the solution.
In the first version, introduced in \citeonline{canbolat}, all the facilities are axis-parallel ellipses making this problem be a slightly modified MCD. Throughout this work, we will refer to this version of the problem as \sigla{MCE}{Maximum Cover by Ellipses}.
In the second version, introduced in \citeonline{andreta}, an angle of rotation is also part of each ellipse's location, making the problem much more challenging.
This version of the problem will be referred to as \sigla{MCER}{Maximum Covering by Ellipses with Rotation}.

The main practical motivation to study these two versions of PMCLP is that cellphone towers can have an elliptically shaped coverage area, therefore, to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by their signal, an elliptical PMCLP is better-suited \cite{canbolat}.

It is fair to say that PMCLP with elliptical coverage has not been studied a lot as only two articles have been found on it. In \citeonline{canbolat}, a mixed-integer non-linear programming method was proposed as a first approach to the problem. For some instances, the method took too long and did not find an optimal solution. Because of that, a heuristic method was developed using a technique called Simulated Annealing, which was able to obtain solutions for the instances proposed in that study.
The problem was further explored in \citeonline{andreta}, which introduced the version where the ellipses can be freely rotated, to which an exact and a heuristic method was proposed, and developed a new method for the axis-parallel version of the problem, which was able to obtain optimal solutions for instances that the method proposed by \citeonline{canbolat} could not.
The exact method for the version with rotation could not obtain optimal solutions within a predefined time limit for several instances, the heuristic method though, returned solutions for every instance, and impressively enough, obtained optimal solutions for every verifiable instance.

The main results of this work are presented in \autoref{chapter:mcer}, where a new algorithm for MCER is developed. 
In the numerical experiments displayed in \autoref{chapter:numerical}, this algorithm shoed very good performance and even obtained optimal solutions for instances that the heuristic method proposed in \citeonline{andreta} reported non-optimal ones. 
In the development of the algorithm for MCER in \autoref{chapter:mcer}, a subproblem in which no prior study could be found surged. The whole \autoref{chapter:e3p} is devoted to the creation of an algorithm for that problem.
The rest of the work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximum covering by disks problem is studied, and an algorithm is proposed for it; in \autoref{chapter:mce}, the maximum covering by ellipses is introduced, and the algorithm for the disks case is adapted for it; in \autoref{chapter:numerical}, numerical experiments are analyzed, and implementation details are given; finally, \autoref{chapter:future_work} presents a conclusion as well as what is left as future work.

### 2020-03-01 defesa/tex/chapter/mcd.tex
wip

Then, with \autoref{algoritmo:mcd_cls}, an algorithm for MCD that checks every possible center for every disk yields a $\bigO(n^{2m})$ run-time complexity.
This algorithm is described in \autoref{chapter:ellipses} for the axis-parallel ellipses case.

@@

\begin{algoritmo}
	\caption{Algorithm for MCD1 that returns a CLS.}\label{algoritmo:mcd_cls}
	\begin{algorithmic}[1]
		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$ with weights $\Ww=\{w_1, \dots, w_n\}$, and a radius $r\in\R_{>0}$.}
		\Ensure{A CLS for the disk given by radius $r$.}

>>>>

Then, with \autoref{algoritmo:mcd_cls}, an algorithm for MCD that checks every possible center for every disk yields a $\bigO(n^{2m})$ run-time complexity.
This algorithm is described in \autoref{chapter:mce} for the axis-parallel ellipses case.

@@

\begin{algoritmo}
	\caption{Algorithm for that returns a CLS given a radius and a demand set.}\label{algoritmo:mcd_cls}
	\begin{algorithmic}[1]
		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$ with weights $\Ww=\{w_1, \dots, w_n\}$, and a radius $r\in\R_{>0}$.}
		\Ensure{A CLS for the disk given by radius $r$.}
